A boundary-integral framework to simulate \\ the viscous erosion of a porous medium

### 2018-04-06 docs/methods/erosion_methods.tex
NM
small changes

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction\label{s:intro}}
Flow-induced erosion deteriorates and reshapes solid material over a range of scales found in nature, from large geological formations~\cite{han1969, Rothman2012, coh-dev-sey-yi-szy-rot2015}, down to human-scale features and patterns~\cite{daerr2003erosion}. Though less visible, these same forces are at work at the very smallest scales, slowly deteriorating the individual constituents of porous media (e.g.~solid, sand, or clay) or biological structures like plaque and biofilms~\cite{pic-van-hei2000, sha2002, gro-gij-van-fer-hat-van-yua-wen2007}. Motivated by such applications, we develop numerical methods to simulate fluid-mechanical erosion of multiple solid bodies in Stokes flow --- the most relevant regime for groundwater and bio-fluid applications.

@@

\paragraph{Contributions}
The methods developed here will allow us to simulate the erosion of many bodies, as demonstrated in Fig.~\ref{fig:50bodies} for the case of 50 bodies (of randomly assigned initial sizes and positions). Here, the erosion of solid material arises from the mechanical stress induced by the surrounding flow. In particular, we take the local rate of erosion to be proportional to the magnitude of the shear stress --- a law that has been verified by laboratory experiments~\cite{ris-moo-chi-she-zha2012}. As seen in Fig.~\ref{fig:50bodies}, erosion not only diminishes the size of the bodies, but also alters their shapes considerably. Notice, in particular, that many bodies develop corner-like features and nearly flat faces, with straight channels intervening between them. In the figure, color represents the vorticity of the surrounding flow, which reduces to shear on solid boundaries and thus provides a convenient tool for visualizing local erosion rates.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vsp{2}
The present study develops numerical methods to simulate erosion of multiply-connected two-dimensional geometries. In this fashion, individual pores are resolved rather than homogenized.  A boundary integral equation (BIE) is used to solve the incompressible Stokes equations in the complex geometry.  The resulting method resolves individual grains and the non-negligible interactions between bodies.  To link the eroding body and fluid dynamics, the body is eroded in the normal direction at a rate that is proportional to the magnitude of the shear stress.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction\label{s:intro}}
Flow-induced erosion deteriorates and reshapes solid material over a range of scales found in nature, from large geological formations~\cite{han1969, Rothman2012, coh-dev-sey-yi-szy-rot2015}, down to human-scale features and patterns~\cite{daerr2003erosion}. Though less visible, these same forces are at work at the very smallest scales, slowly deteriorating the individual constituents of porous media (e.g.~solid, sand, or clay) or biological structures like plaque and biofilms~\cite{pic-van-hei2000, sha2002, gro-gij-van-fer-hat-van-yua-wen2007}. Motivated by such applications, we develop numerical methods to simulate fluid-mechanical erosion of multiple solid bodies in Stokes flow---the most relevant regime for groundwater and bio-fluid applications.

@@

The methods developed here will allow us to simulate the erosion of many bodies, as demonstrated in Fig.~\ref{fig:50bodies} for the case of 50 bodies (of randomly assigned initial sizes and positions). Here, the erosion of solid material arises from the mechanical stress induced by the surrounding flow. In particular, we take the local rate of erosion to be proportional to the magnitude of the shear stress---a law that has been verified by laboratory experiments~\cite{ris-moo-chi-she-zha2012}. As seen in Fig.~\ref{fig:50bodies}, erosion not only diminishes the size of the bodies, but also alters their shapes considerably. Notice, in particular, that many bodies develop corner-like features and nearly flat faces, with straight channels intervening between them. In the figure, color represents the vorticity of the surrounding flow, which reduces to shear on solid boundaries and thus provides a convenient tool for visualizing local erosion rates.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
To solve the incompressible Stokes equations in the complex geometry, we
employ a boundary integral equation (BIE) method.
The present study develops numerical methods to simulate erosion of multiply-connected two-dimensional geometries. In this fashion, individual pores are resolved rather than homogenized.  A boundary integral equation (BIE) is used to solve the incompressible Stokes equations in the complex geometry.  The resulting method resolves individual grains and the non-negligible interactions between bodies.  To link the eroding body and fluid dynamics, the body is eroded in the normal direction at a rate that is proportional to the magnitude of the shear stress.
